---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
    citation_package: natbib
    template: C:/Users/meglarse/Dropbox (Personal)/Consulting/Salk_Kateri/modIteration-report/doc-setup/svm-latex-ms-mod.tex
title: Fe-ELA Model Iteration Comparison Report [Iteration Number]
author: 
- name: Dr. Kateri Salk
  affiliation: University of Waterloo
geometry: margin=0.5in
fontsize: 11pt
fontfamily: mathpazo
biblio-style: apsr
---

<Information in these brackets is used for annotating the RMarkdown file. They will not appear in the final PDF version of the document>

<Setup the global options for the R chunks in your document>
```{r setup, include=FALSE}

setwd("/Users/krsalkgu/Documents/MATLAB/KRS_ELA_Model/L227_application/Model Output Evaluations")

# Install packages for the document

## install.packages("ggplot2")
library(ggplot2)

# Package options
library(knitr)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

## ggplot theme and figure parameters
theme_std <- function (base_size = 16, base_family = "") {
    theme_grey(base_size = base_size, base_family = base_family) %+replace% 
        theme(axis.ticks = element_line(colour = "black", size = 1), 
              legend.key = element_rect(colour = "white"), 
              panel.background = element_rect(fill = "white", colour = NA), 
              panel.border = element_rect(fill = NA, colour = NA),
              axis.line = element_line(size = 0.5, colour = "black"),
              panel.grid.major = element_line(NA), 
              panel.grid.minor = element_line(NA), 
              strip.background = element_rect(fill = "grey80", colour = "grey50", size = 0.2),
              axis.text  = element_text(size=rel(0.9)),
              axis.title.x = element_text(margin = unit(c(3, 0, 0, 0), "mm"),size=rel(1)),
              axis.title.y = element_text(margin = unit(c(0, 3, 0, 0), "mm"),size=rel(1), angle = 90),
              strip.text = element_text(size = rel(1.15), colour = "black", face = "bold"),
              plot.margin=unit(c(10,10,10,10),"pt")
        )
}

theme_set(theme_std())

#test.plot <- ggplot(mtcars, aes(x = hp , y = mpg, col = mpg)) +
#  geom_point()
#print(test.plot)
```

# Summary of Major Findings

1. **Model overlay** was ok...(\autoref{ModelOverlay}) <we can use the function autoref to automatically pull labeled graphics>
    + Sublists can be made like this

2. **Model regression** was ok...(\autoref{ModelRegression}) <we can use the function autoref to automatically pull labeled graphics>
    + Sublists can be made like this

<Add the text for each of your sections. Check out the [RMarkdown cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) and [Markdown cheatsheet](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet#lists) for more information about text formatting.>

\newpage

# Model Overlay

<Perform the required functions to match the model output and observational data>
```{r data-reduction, echo = FALSE}
# Read in the data and add colnames
obs <- read.csv("Observed_IntegratedEpi.csv", header = T)
attach(obs)
colnames(obs) <- c("org.date","Year","Month","Day", "obs.TP","obs.chla","obs.TDP")

obs_temp <- read.csv("Observed_Temperature.csv")
attach(obs_temp)

mod <- read.csv("Output_IntegratedEpi.csv", header = F)
colnames(mod) <- c("Year","Month","Day","ML.date","mod.chla","mod.TDP","mod.TP", "mod.Temp1m", "mod.Temp4m", "mod.Temp9m")

#Let's tidy! - part 1
library(tidyr)
library(magrittr)
obs <- obs %>% 
  unite(date, Year, Month, Day, sep = '-') #%>%
  #filter(!is.na(obs.TP))
obs <- data.frame(obs, Month, Year)
obs <- na.omit(obs)
obs <- obs[,-1]



mod <- mod %>% unite(date, Year, Month, Day, sep = '-')
mod <- mod[,-2]

# Convert time object
obs$date <- as.Date(obs$date, format = "%Y-%m-%d") #Converts data to date structure
obs_temp$date <- as.Date(obs_temp$date) #, format = "%Y-%m-%d") #Converts data to date structure
mod$date <- as.Date(mod$date, format = "%Y-%m-%d") #Converts data to date structure

# tidy! - part 2: match model time and observational time
library(dplyr)
mod.match <- inner_join(obs,mod, by = "date") 
mod.match.temp <- inner_join(obs_temp, mod, by = "date")
obs.totaltempa <- data.frame(cbind(mod.match.temp$obs.Temp1m, mod.match.temp$obs.Temp4m, mod.match.temp$obs.Temp9m))
obs.totaltemp <- stack(obs.totaltempa)
mod.totaltempa <- data.frame(cbind(mod.match.temp$mod.Temp1m, mod.match.temp$mod.Temp4m, mod.match.temp$mod.Temp9m))
mod.totaltemp <- stack(mod.totaltempa)
totaltemp <- data.frame(cbind(obs.totaltemp[,1], mod.totaltemp[,1]))
colnames(totaltemp) <- c("TempObs","TempMod")

#write data for later use
#write.csv(filename = paste0("./example-data/processed/", format(Sys.time(), "%Y%m%d-%H%M"), "_modelcomp-output.csv"))
```

<Figure 1>
```{r model-overlay, fig.cap="Overlay of observed (red) and modeled data (black). \\label{ModelOverlay}", echo = FALSE, fig.height = 7}

p <- ggplot(mod.match, aes(x = date)) +
  geom_point(aes(y = obs.TP, col = "Observed"), pch = 19, size = 1) +
  geom_line(aes(y = mod.TP, col = "Modeled"), size = 0.5) +
  ylim(0,150) +
  ylab(expression(Total ~ Phosphorus ~ (mu*g / L))) +
  xlab(" ") +
  scale_colour_manual("", 
                      breaks = c("Observed", "Modeled"),
                      values = c("black", "red")) +
  theme(legend.position = c(0.9,0.9))
#print(p)


p2 <- ggplot(mod.match, aes(x = date)) +
  geom_point(aes(y = obs.TDP, col = "Observed"), pch = 19, size = 1) +
  geom_line(aes(y = mod.TDP, col = "Modeled"), size = 0.5) +
  ylim(0,50) +
  ylab(expression(TDP ~ (mu*g / L))) +
  xlab(" ") +
  scale_colour_manual("", 
                      breaks = c("Observed", "Modeled"),
                      values = c("black", "red")) +
  theme(legend.position = c(0.9,0.9))
#print(p2)

p3 <- ggplot(mod.match, aes(x = date)) +
  geom_point(aes(y = obs.chla, col = "Observed"), pch = 19, size = 1) +
  geom_line(aes(y = mod.chla, col = "Modeled"), size = 0.5) +
  ylim(0,100) +
  ylab(expression(Chlorophyll ~ a ~ (mu*g / L))) +
  xlab(" ") +
  scale_colour_manual("", 
                      breaks = c("Observed", "Modeled"),
                      values = c("black", "red")) +
  theme(legend.position = c(0.9,0.9))
#print(p3)

p4 <- ggplot(mod.match.temp, aes(x = date)) +
  geom_point(aes(y = obs.Temp1m, col = "Observed"), pch = 19, size = 1) +
  geom_line(aes(y = mod.Temp1m, col = "Modeled"), size = 0.5) +
  ylim(0,30) +
  ylab(expression("Temperature " ( degree*C))) +
  xlab(" ") +
  scale_colour_manual("", 
                      breaks = c("Observed", "Modeled"),
                      values = c("black", "red")) +
  theme(legend.position = c(0.9,0.9))

p5 <- ggplot(mod.match.temp, aes(x = date)) +
  geom_point(aes(y = obs.Temp4m, col = "Observed"), pch = 19, size = 1) +
  geom_line(aes(y = mod.Temp4m, col = "Modeled"), size = 0.5) +
  ylim(0,30) +
  ylab(expression("Temperature " ( degree*C))) +
  xlab(" ") +
  scale_colour_manual("", 
                      breaks = c("Observed", "Modeled"),
                      values = c("black", "red")) +
  theme(legend.position = c(0.9,0.9))
  
p6 <- ggplot(mod.match.temp, aes(x = date)) +
  geom_point(aes(y = obs.Temp9m, col = "Observed"), pch = 19, size = 1) +
  geom_line(aes(y = mod.Temp9m, col = "Modeled"), size = 0.5) +
  ylim(0,10) +
  ylab(expression("Temperature " ( degree*C))) +
  xlab(" ") +
  scale_colour_manual("", 
                      breaks = c("Observed", "Modeled"),
                      values = c("black", "red")) +
  theme(legend.position = c(0.9,0.9))

require(gridExtra)
grid.arrange(p, p2, p3, ncol = 1)

```

\newpage

# Model regression

```{r model-reg, fig.cap="Data regression for observed against modeled data. \\label{ModelRegression}", echo = FALSE, fig.height = 5}

mod.lm <- lm(mod.match$mod.TP ~ mod.match$obs.TP)
summary(mod.lm)
mse <- mean(residuals(mod.lm)^2)
rmse <- sqrt(mse)
p <- ggplot(mod.match, aes(x = obs.TP, y = mod.TP, color=Month)) +
  geom_point(pch = 19, size = 1.5) +
  geom_abline(slope=1, intercept=0) + 
  scale_x_continuous(limits=c(0,100)) + scale_y_continuous(limits=c(0,100)) +
  xlab(expression(Total ~ Phosphorus ~ Observed ~ (mu*g / L))) +
  ylab(expression(Total ~ Phosphorus ~ Modeled ~ (mu*g / L))) +

  scale_color_distiller(palette="YlGnBu") +
  theme(legend.position=c(0.9, 0.8))
  
#print(p)


mod.lm <- lm(mod.match$mod.TDP ~ mod.match$obs.TDP)
summary(mod.lm)
mse <- mean(residuals(mod.lm)^2)
rmse <- sqrt(mse)
p2 <- ggplot(mod.match, aes(x = obs.TDP, y = mod.TDP, color=Month)) +
  geom_point(pch = 19, size = 1.5) +
  geom_abline(slope=1, intercept=0) + 
   scale_x_continuous(limits=c(0,50)) + scale_y_continuous(limits=c(0,50)) +
  xlab(expression(TDP ~ Observed ~ (mu*g / L))) +
  ylab(expression(TDP ~ Modeled ~ (mu*g / L))) +
  scale_color_distiller(palette="YlGnBu") +
  theme(legend.position=c(0.9, 0.8))
#print(p2)

mod.lm <- lm(mod.match$mod.chla ~ mod.match$obs.chla)
summary(mod.lm)
mse <- mean(residuals(mod.lm)^2)
rmse <- sqrt(mse)
p3 <- ggplot(mod.match, aes(x = obs.chla, y = mod.chla, color=Month)) +
  geom_point(pch = 19, size = 1.5) +
  geom_abline(slope=1, intercept=0) + #(intercept = mod.lm[[1]][[1]], slope = mod.lm[[1]][[2]]) +
  scale_x_continuous(limits=c(0,100)) + scale_y_continuous(limits=c(0,100)) +
  xlab(expression(Chlorophyll ~ a ~ Observed ~ (mu*g / L))) +
  ylab(expression(Chlorophyll ~ a ~ Modeled ~ (mu*g / L))) +
  scale_color_distiller(palette="YlGnBu") +
  theme(legend.position=c(0.9, 0.8))
#print(p3)

mod.lm <- lm(mod.match$mod.chla ~ mod.match$obs.chla)
summary(mod.lm)
mse <- mean(residuals(mod.lm)^2)
rmse <- sqrt(mse)
p4 <- ggplot(mod.match, aes(x = obs.chla, y = mod.chla, color=Year)) +
  geom_point(pch = 19, size = 1.5) +
  geom_abline(slope=1, intercept=0) + 
  scale_x_continuous(limits=c(0,100)) + scale_y_continuous(limits=c(0,100)) +
  xlab(expression(Chlorophyll ~ a ~ Observed ~ (mu*g / L))) +
  ylab(expression(Chlorophyll ~ a ~ Modeled ~ (mu*g / L))) +

  scale_color_distiller(palette="YlGnBu") +
  theme(legend.position=c(0.9, 0.8))

p5 <- ggplot(mod.match, aes(x = obs.TP, y = mod.TP, color=Year)) +
  geom_point(pch = 19, size = 1.5) +
  geom_abline(slope=1, intercept=0) + 
  scale_x_continuous(limits=c(0,100)) + scale_y_continuous(limits=c(0,100)) +
  xlab(expression(TP ~ Observed ~ (mu*g / L))) +
  ylab(expression(TP ~ Modeled ~ (mu*g / L))) +
  scale_color_distiller(palette="YlGnBu") +
  theme(legend.position=c(0.9, 0.8))

tempregression <- lm(totaltemp$TempObs ~ totaltemp$TempMod)
summary(tempregression)
mse <- mean(residuals(tempregression)^2)
rmse <- sqrt(mse)
rmse
p6 <- ggplot(totaltemp, aes(x = TempObs, y = TempMod)) +
  geom_point(pch = 19, size = 1.5) +
  geom_abline(slope=1, intercept=0) + 
  scale_x_continuous(limits=c(0,30)) + scale_y_continuous(limits=c(0,30)) +
  xlab(expression("Temperature Observed " ( degree*C))) +
  ylab(expression("Temperature Modeled " ( degree*C))) +
  scale_color_distiller(palette="YlGnBu") +
  theme(legend.position=c(0.9, 0.8))

library(gridExtra)
grid.arrange(p, p2, p3, ncol = 2)

```


\newpage

# Additional information
## Model Parameters
```{r}
parms <- read.csv("./example-data/L227_para_all.csv", header = F)
colnames(parms) <- c("Parameter","Value","Min","Max","Unit")
parms <- parms[-c(1:2),]

require(pander)
row.names(parms) <- NULL
panderOptions("graph.fontsize", 8)
pander(parms, include.rownames=FALSE)
```

\newpage

# Next steps and follow-up questions
1. Let's change the vmax in the next interation.

